Abstract Binding Trees

### 2015-11-01 paper.tex
Fix symbol-related bugs

For a presheaf $A:\widehat{\HypCat}$ and a sort-indexed family of presheaves
$P:\widehat{\HypCat}^\Sorts$, we have an operation $A\bullet P$,
defined as a coend in the following way:
\[
  \Define{(A\bullet P)(\Upsilon\parallel\Gamma)}{
    \int^{\Delta\in\OpCat\Ctx}
      A(\Upsilon\parallel\Delta)
      \times \prod_{x\in\Dom\Delta} P_{\Delta(x)}(\Upsilon\parallel\Gamma)
  }
\]

@@

Then, the variables object
$\Define{V_s(\Upsilon\parallel\Gamma)}{\MkSet{x\in\Dom\Gamma\mid \Gamma(x)=s}}$
is the unit to this tensor; additionally, we have a presheaf of symbols
$\Define{Y_s(\Upsilon\parallel\Gamma)}{\MkSet{u\in\Dom\Upsilon\mid
\Upsilon(x)=s}}$. We will say that an object
$\Of{P}{\widehat{\HypCat}^\Sorts}$ is a $\Sigma$-monoid in case it is equipped
with the following natural transformations where $\nu$ embeds variables into
$P$ and $\varsigma$ equips $P$ with an operation for simultaneous substitutions
of variables.

@@

For an object $\Of{P}{\widehat{\HypCat}^\Sorts}$, we will use the notation
$P^{[\Gamma]}$ to mean $\prod_{x\in\Dom\Gamma}P_{\Gamma(x)}$; likewise,
$Y^{\{\Upsilon\}}$ shall mean $\prod_{u\in\Dom\Upsilon}Y_{\Upsilon(u)}$.
Additionally, we have an induced map $\Of{\nu_\Gamma}{V^{[\Gamma]}\to
P^{[\Gamma]}}$.

@@

\[
  \Define{
    \SemBrackets{
      \Omega\triangleright\Upsilon\parallel\Gamma
    }_P
  }{
    \left(\prod_{(\MV{m}:\MkValence{\vec{p}}{\vec{q}}{s})\in\Omega}
    P_{s}^{\Yoneda{\vec{p}\parallel\vec{q}})}\right)
    \times
    Y^{\{\Upsilon\}}
    \times
    V^{[\Gamma]}
  }
\]

We define the interpretation of a term $M$ in the model $P$ as a morphism
$\Of{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash
M:s}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P\to P_s}$.
The interpretation of a variable
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x_j:s}_P$ is
the following composite:

\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_3}"]
    \& {\IMode{V^{[\Gamma]}}} \arrow[r, "\IMode{\nu_{\Gamma}}"]
    \& {\IMode{P^{[\Gamma]}}} \arrow[r, "\IMode{\pi_j}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{var}
\]

The interpretation of metavariable applications
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash
\MApp{\MV{m}_i}{u_0,\dots,u_m}{M_0,\dots,M_n} : s}_P$, where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{p}}{\vec{q}}{s}}$, is the following composite
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=large]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\Tuple{\pi_i\,\pi_1, \phi}}"]
    \& {\IMode{P_{s'}^{\Yoneda{\vec{p}\parallel\vec{q}}} \times P^{[\vec{q}]}}} \arrow[r, "\IMode{\varsigma_{\vec{q}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\[
  \Define{\phi}{
    \Tuple{
      \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M_j:q_j}_P
    }_{j\leq n}
  }
\]

>>>>

Let $\Define{V_s(\Upsilon\parallel\Gamma)}{\MkSet{x\in\Dom\Gamma\mid
\Gamma(x)=s}}$ be called the presheaf of variables; additionally, we have a
presheaf of symbols
$\Define{Y_s(\Upsilon\parallel\Gamma)}{\MkSet{u\in\Dom\Upsilon\mid
\Upsilon(x)=s}}$. For an object $\Of{P}{\widehat{\HypCat}^\Sorts}$, we will
use the notation $P^{[\Gamma]}$ to mean $\prod_{x\in\Dom\Gamma}P_{\Gamma(x)}$;
likewise, $Y^{\{\Upsilon\}}$ shall mean
$\prod_{u\in\Dom\Upsilon}Y_{\Upsilon(u)}$.

For a presheaf $A:\widehat{\HypCat}$ and a sort-indexed family of presheaves
$P:\widehat{\HypCat}^\Sorts$, we have an operation $A\bullet P$,
defined as a coend in the following way:
\[
  \Define{(A\bullet P)(\Upsilon\parallel\Gamma)}{
    \int^{(\Upsilon'\parallel\Delta)\in\HypCat}
      A(\Upsilon'\parallel\Delta)
      \times Y^{\{\Upsilon'\}}(\Upsilon\parallel\Gamma)
      \times P^{[\Delta]}(\Upsilon\parallel\Gamma)
  }
\]

@@

Then, $V$ is the unit to this tensor. We will say that an object
$\Of{P}{\widehat{\HypCat}^\Sorts}$ is a $\Sigma$-monoid in case it is equipped
with the following natural transformations where $\nu$ embeds variables into
$P$ and $\varsigma$ equips $P$ with an operation for simultaneous substitutions
of variables.

@@

%%TODO
We also have an induced maps $\Of{\nu_\Gamma}{V^{[\Gamma]}\to P^{[\Gamma]}}$
and
$\Of{\varsigma_{\Upsilon\parallel\Gamma}}{A^{\Yoneda{\Upsilon\parallel\Gamma}} \times
Y^{\{\Upsilon\}}\times A^{[\Gamma]}}$.

@@

The metavariable, symbol and variable contexts are interpreted in a model $P$ as an
environment presheaf in the following way:
\[
  \Define{
    \SemBrackets{
      \Omega\triangleright\Upsilon\parallel\Gamma
    }_P
  }{
    \left(\prod_{(\MV{m}:\MkValence{\vec{p}}{\vec{q}}{s})\in\Omega}
    P_{s}^{\Yoneda{\vec{p}\parallel\vec{q}})}\right)
    \times
    Y^{\{\Upsilon\}}
    \times
    V^{[\Gamma]}
  }
\]

Then, the interpretation of a term in a model $P$ is a map from its environment
to $P$, that is,
$\Of{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash
M:s}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P\to P_s}$.
The interpretation of a variable
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x_j:s}_P$
simply projects it of the environment and embeds it into the
model, as follows:
\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_3}"]
    \& {\IMode{V^{[\Gamma]}}} \arrow[r, "\IMode{\nu_{\Gamma}}"]
    \& {\IMode{P^{[\Gamma]}}} \arrow[r, "\IMode{\pi_j}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{var}
\]

The interpretation of metavariable applications
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash
\MApp{\MV{m}_i}{u_0,\dots,u_m}{M_0,\dots,M_n} : s}_P$, where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{p}}{\vec{q}}{s}}$, proceeds by projecting the metavariable's interpretation from the environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_i\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{s'}^{\Yoneda{\vec{p}\parallel\vec{q}}}\times Y^{\{\vec{p}\}} \times P^{[\vec{q}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{p}\parallel\vec{q}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
    \Dom{\vec{p}}\mapsto \vec{u}
  }\\
  \ADefine{\psi}{
    \Tuple{
      \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M_j:q_j}_P
    }_{j\leq n}
  }
\end{align*}
